### 2017-05-05 abstract.tex
need to cut a half page

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application, determining similarity of failing test cases, for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original compiler) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original compiler) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

### 2017-05-05 experiments.tex
need to cut a half page

All mutants were produced using the C mutation tool written by Jamie Andrews \cite{mutant}, used in many previous experiments in mutation analysis and software testing.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  Coverage was analyzed with gcov.   All experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7 (not using the second core); GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the 2013 PLDI paper no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the PLDI 2013 data failed in the new environment, representing 28 distinct faults.

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our hypotheses.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.  This is only a moderately strong oracle, and allows serious deviations from both the JavaScript language specification and normal SpiderMonkey behavior, while checking some complex details, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely --- only missed optimizations are allowed.

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering with our metrics, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutant makes it 0.6 times as likely they are due to the same fault.  Matching non-repair, however, provides very weak evidence:  only a 34.14\% chance of matching fault, just over baseline probability.

@@

Table \ref{jstable} shows a comparison of three fault localization methods for the SpiderMonkey faults.  The first column shows, for each fault, identified by the commit number of the code change that first ``fixed'' the failing tests associated with the fault, its FPF ranking: this is \emph{not} a fault localization ranking, just a way to see that the localization success seems to be somewhat independent of the ease of distinguishing the failures for a fault.  The next four columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The four rankings are: the {\bf Coverage} localization, the {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that repair a failure but also break some passing test, is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.

Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine coverage changes and mutants.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seem unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c||c|c|c|c|}
\hline
& & \multicolumn{4}{|c|}{Localization Rank} \\
\hline
Fault & FPF & Coverage & Repair & MUSE & MUSEUM \\
\hline
880 & 1 & 2,255 & - & - & - \\
95 & 6 & 720 & - & 173 & -\\
1294 & 9 & 190 & 1 & 22 & 4 \\
60 & 10 & - & - & - & -\\
1543 & 15 & 18 & 19 & 118 & 26\\
1172 & 19 & 46 & 28 & 87 & 23\\
1561 & 106 & - & - & - & - \\
115 & 192 & 6 & 3 & 133 & 5 \\
\hline
\end{tabular}
}
\caption{Fault localization results for SpiderMonkey}
%\vspace{-0.2in}
\label{jstable}
\end{table}

@@

The first thing to note about results is that Table \ref{jstable} only includes 8 of the 28 SpiderMonkey faults.  This is due to a problem discussed in the paper introducing this data set:  producing ground truth patches for a large application, in the sense of finding a minimal, clearly fault-fixing code change that can be back-ported to the original code is difficult \cite{PLDI13}.  While we believe the 28 faults identified in the PLDI 2013 data set are correct, it is very difficult to produce a valid patch of version 1.6 that captures the fix for most of these faults.  In some cases the final commit that caused tests to stop failing appeared to only be the end of a complex series of changes that converged on a correct fix.  In other cases, the code was modified so extensively before the fix that identifying ``the incorrect part'' of the original code seemed to owe more to guesswork than certainty.  The evaluation of localization therefore only examines the 8 faults for which we could be reasonably certain that the patch to 1.6 was correct and characterized the fault in question accurately.  The smallest patch required modification of two statements, and was thus larger than any mutants applied.  In no case was the patch equivalent to one of the mutants.

No method performs extremely well --- for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in the first 20 to 30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Coverage} performs very badly for three faults, does not manage to be useful by our definition for another, and in the remaining two cases provides a good localization, in one case the best.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c||c|c|c|c|}
\hline
& & \multicolumn{4}{|c|}{Localization Rank} \\
\hline
Fault & FPF & Coverage & Repair & MUSE & MUSEUM \\
\hline
139094 & 1 & 44,561 & - & 157 & -\\
133004 & 2 & 75 & 1 & 99 & 14\\
158782 & 4 & - & - & 146 & -\\
156496 & 5 & 3,067 & - & - & -\\
143677 & 7 & 186 & - & 109 & -\\
158555 & 8 & 490 & - & - & -\\
134321 & 10 & - & - & - & -\\
133940 & 14 & 260 & 4 & 158 & 18\\
141195 & 15 & 465 & - & - & -\\
156795 & 17 & 19 & - & - & -\\
139709 & 19 & 43,903 & 10 & 167 & 6\\
155698 & 22 & 85 & 1 & 172 & 195\\
138646 & 24 & 2 & - & - & -\\
140795 & 25 & 302 & 34 & 170 & 125\\
136501 & 44 & 223 & 5 & 159 & 31\\
134322 & 45 & 639 & - & - & -\\
\hline
\end{tabular}
}
\caption{Fault localization results for GCC}
\label{gcctable}
\end{table}

Table \ref{gcctable} shows localization results for GCC 4.3.0.  Again, only some faults were deemed to have a strong enough ground truth patches for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but usually performed poorly.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed very well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists, and results in {\bf Repair} either providing a ``useful'' localization or no localization at all, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  For the MUSEUM data set, there are no cases with multiple faults for our method to use to further distinguish repairs, so its similarity to MUSEUM in results is not surprising (in this context, our approach is essentially MUSEUM modified to throw out any repairs that cause previously passing tests to fail).

Finally, in contrast to many previously reported results in fault localization, typically over much simpler programs and faults than subtle compiler semantics bugs, all methods frequently failed to provide a useful localization at all.  This is presumably due to the difficulty of compiler bugs:  our approach, and MUSEUM, performed very well on complex multi-lingual faults in the MUSEUM data set.  In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.

@@

Second, and most critically, most program mutants never need to be considered as repairs, because we only consider mutants that cause no passing test case to fail.  MUSE and MUSEUM use kills by passing tests to help rank such tests as repairs, which is finer grained but more expensive.  As we show, MUSE and MUSEUM \emph{can}  be used without passing tests or these mutants, and MUSEUM still produces good results even with a weak oracle and few operators.  MUSE, MUSEUM, and our approach all run analysis without coverage instrumentation; we re-run repaired tests under gcov when using the {\bf Coverage} localization.

>>>>

We applied our metric to two of the datasets used in the previous study of compiler fuzzer taming \cite{PLDI13}: faults and tests cases for SpiderMonkey 1.6, Mozilla's JavaScript engine, with tests generated by {\tt jsfunfuzz} \cite{jsfunfuzz}, and \emph{wrong code} faults and test cases for GCC 4.3.0, with tests generated by Csmith \cite{csmith}.   We did not use the crash faults from that data set, as these are in practice fairly easy to identify by hand (and perfectly identified by previous metrics), and also typically easy to debug.

Our mutants were produced using the tool written by Jamie Andrews \cite{mutant}.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  Experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7; GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the 2013 PLDI paper no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the PLDI 2013 data failed in the new environment, representing 28 distinct faults.

These data sets, though similar in that both compilers are written in C, provide some interesting variance for testing our metrics.  The oracle for SpiderMonkey executions is the set of checks built in to {\tt jsfunfuzz} plus the requirement that the execution not crash.  This is only a moderately strong oracle, and allows serious deviations from both the JavaScript language specification and normal SpiderMonkey behavior, while checking some complex details, such as {\tt eval} round-trips.  For GCC, the oracle is a differential check on a hash code:  failure was defined as producing a executable with the -O3 flag that, when executed, produced a different checksum than code compiled by either of GCC 4.9.3 or clang 7.0.0, both using -O0.  A repairing mutant must enable GCC 4.3.0 to actually compile code correctly, which is a very strict correctness property, making coincidental correctness \cite{CCT} highly unlikely --- only missed optimizations are allowed.

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering with our metrics, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  We confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutant makes it 0.6 times as likely they are due to the same fault.  Matching non-repair, however, provides very weak evidence:  only a 34.14\% chance of matching fault, just over baseline.

@@

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column shows, for each fault, an ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that repair a failure but also break some passing test, is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests until at least a single kill was observed took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.

\comment{
Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine coverage changes and mutants.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seem unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.
}

\comment{
\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c|c|}
\hline
%& \multicolumn{3}{|c|}{Localization Rank} \\
%\hline
Fault & Repair & MUSE & MUSEUM \\
\hline
880 & - & - & - \\
95 & - & 173 & -\\
1294 & 1 & 22 & 4 \\
60 & - & - & -\\
1543 & 19 & 118 & 26\\
1172 & 28 & 87 & 23\\
1561 & - & - & - \\
115 & 3 & 133 & 5 \\
\hline
\end{tabular}
}
\caption{Fault localization results for SpiderMonkey}
%\vspace{-0.2in}
\label{jstable}
\end{table}
}

@@

Table \ref{bothtable} only includes 8 of the 28 SpiderMonkey faults.  This is due to a problem with the data set:  producing ground truth patches for a large application, in the sense of finding a minimal, clearly fault-fixing code change that can be back-ported to the original code is difficult \cite{PLDI13}.  While we believe the 28 faults identified in the PLDI 2013 data set are correct, it is very difficult to produce a valid patch of version 1.6 that captures the fix for most of these faults.  In some cases the final commit that caused tests to stop failing appeared to only be the end of a complex series of changes that converged on a correct fix.  In other cases, the code was modified so extensively before the fix that identifying ``the incorrect part'' of the original code seemed to owe more to guesswork than certainty.  The evaluation of localization therefore only examines the 8 faults for which we could be reasonably certain that the patch to 1.6 was correct and characterized the fault in question accurately.  In no case was the patch equivalent to one of the mutants (the smallest patch modified two statements).

No method performs extremely well --- for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in the first 25-30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

\comment{
\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c||c|c|}
\hline
%& & \multicolumn{4}{|c|}{Localization Rank} \\
%\hline
Fault & Repair & MUSE & MUSEUM \\
\hline
139094 & - & 157 & -\\
133004 & 1 & 99 & 14\\
158782 & - & 146 & -\\
156496 &  - & - & -\\
143677 & - & 109 & -\\
158555 & - & - & -\\
134321 & - & - & -\\
133940 & 4 & 158 & 18\\
141195 & - & - & -\\
156795 & - & - & -\\
139709 & 10 & 167 & 6\\
155698 & 1 & 172 & 195\\
138646 & - & - & -\\
140795 & 34 & 170 & 125\\
136501 &  5 & 159 & 31\\
134322 & - & - & -\\
\hline
\end{tabular}
}
\caption{Fault localization results for GCC}
\label{gcctable}
\end{table}
}

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c|c||c||c|c|c|}
\hline
%& & \multicolumn{4}{|c|}{Localization Rank} \\
%\hline
\multicolumn{4}{|c||}{SpiderMonkey}&\multicolumn{4}{|c|}{GCC}\\
\hline
ID& Repair & MUSE & MUSEUM & ID & Repair & MUSE & MUSEUM \\
\hline
1 & - & - & - &         1 & - & 157 & -\\
2 & - & 173 & - &     2 & 1 & 99 & 14\\
3 & 1 & 22 & 4 &       3 & - & 146 & -\\
4 & - & - & - &         4 &  - & - & -\\
5 & 19 & 118 & 26 & 5 & - & 109 & -\\
6 & 28 & 87 & 23 &   6 & - & - & -\\
7 & - & - & - &         7 & - & - & -\\
8 & 3 & 133 & 5 &     8 & 4 & 158 & 18\\
& & & & 9 & - & - & -\\
& & & & 10 & - & - & -\\
& & & & 11 & 10 & 167 & 6\\
& & & & 12 & 1 & 172 & 195\\
& & & & 13 & - & - & -\\
& & & & 14 & 34 & 170 & 125\\
& & & & 15 &  5 & 159 & 31\\
& & & & 16 & - & - & -\\
\hline
\end{tabular}
}
\caption{Fault localization for compiler faults}
\label{bothtable}
\end{table}

Table \ref{bothtable} shows localization results for GCC 4.3.0.  Again, only some faults were deemed to have a strong enough ground truth patches for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 25) localizations.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed very well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

\input{othertools}

@@

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists, and results in {\bf Repair} either providing a ``useful'' localization or no localization at all, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

\comment{
Finally, in contrast to many previously reported results in fault localization, typically over much simpler programs and faults than subtle compiler semantics bugs, all methods frequently failed to provide a useful localization at all.  This is presumably due to the difficulty of compiler bugs:  our approach, and MUSEUM, performed very well on complex multi-lingual faults in the MUSEUM data set.
}
\comment{ In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.  }

@@

Second, and most critically, most program mutants never need to be considered as repairs, because we only consider mutants that cause no passing test case to fail.  MUSE and MUSEUM use kills by passing tests to help rank such tests as repairs, which is finer grained but more expensive.  As we show, MUSE and MUSEUM \emph{can}  be used without passing tests or these mutants, and MUSEUM still produces good results even with a weak oracle and few operators.
